Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
more corrections

Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$
(\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$ \red{, as defined later?}), errors in the numeric
calculations, or roundoffs in the quantisation.  These uncertainties \red{may be [can be?, are?]} 
parametrically expressed by additive terms, resulting in a uncertain model
$\hat{G}(z)$, such that:
%
\begin{equation}
\hat{G}(z)=\frac{G_n(z)+\Delta G_n(z)}{G_d(z)+\Delta G_d(z)},
\end{equation}
%
which will be represented by the following transfer function:
%
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}} : N_G \geq M_G .
\end{equation}
%
Due to the nature of the methods we use for the stability check, we require
that the parametric errors in the plant have the same polynomial order as
the plant itself (\red{other errors [which precisely? all others?]} are ensured to fulfil this property in our
implementation).

In order to simplify the presentation, we employ a notation based on the
coefficients of the polynomials.  Let $\mathcal{P}^{N}$ be a polynomial
domain of order $N$. Let $P \in \mathcal{P}^{M,N}$ be a rational polynomial
$\frac{P_n}{P_d}$, where $P_n \in \mathcal{P}^{M}$ and $P_d \in \mathcal{P}^{N}$.  
For a vector of coefficients
%
\begin{equation}
\vec{P} \in \mathbb{R}^{N+M+2}=[n_{0}\ n_{1}\ \hdots \ n_{M}\ d_{0}\ d_{1}\ \hdots\ d_{N}\ ]^T
\label{eq:coefficients}
\end{equation}
%
and an uncertainty vector 
%
\begin{equation}
\Delta{\vec{P}}=[\Delta{n}_{0}\ \Delta{n}_{1}\ \hdots \ \Delta{n}_{M}\ \Delta{d}_{0}\ \Delta{d}_{1}\ \hdots\ \Delta{d}_{N}\ ]^T \; 
\end{equation}
%
we write $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$.   
In the following we will either represent the functions $G(z)$, $C(z)$, 
or work over their respective coefficients $\vec{G}, \vec{C}$ in vector form.

\red{[I've tried to clean the notations above. BUT: you cannot later add a transfer function with a vector of coefficients! Heresy!]}

@@

A typical digital control system system with continuous plant and discrete
controller is illustrated in Figure~\ref{fig:sampledsystem}.  The DAC and
ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$ \red{[this is an assumption and as such must be stated.]},
$G(s)$ is the continuous-time plant model with parametric additive
uncertainty $\Delta_p \vec{G}_s$ \red{[above you used n, d subscripts, here s?]}, $R(z)$ is the reference signal, $U(z)$ is
the control signal, and $\hat{Y}(z)$ is the output signal affected by the
noises and uncertainties in the closed-loop system.

@@

%
In Figure~\ref{fig:digsystem1}, two sources of uncertainties are
illustrated: parametric uncertainties related to modelling errors, and
uncertainties introduced by quantisations in sampling and holding process,
i.e., ADC and DAC conversions.  Assuming linearity and independence between
these sources, the uncertain model may be rewritten as 
\red{[unclear whether this is over the s or z domain. further there is lack of proper subscripts (n,d,s), as per the notations introduced above.]}
%
\begin{equation}
\label{eq:complete_unc_model}
\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q \vec{G},
\end{equation}
%
where $\Delta_p \vec{G}$ is the term that corresponds to the parametric
uncertainties and $\Delta_q \vec{G}$ is the term that reflects the
quantisation effects on the plant model.

@@

Let $\hat{C}(z)$ be the transfer function of the digital controller
represented using this FWL with integer size $I$ and fractional size~$F$. 
We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F
\rangle$
%
%Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
%domain, {\it i.e.} a Fixed-Point Finite Word Length with integer size $I$ and fractional
%size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
%
and assume that there exists a function
$\mathit{FWL}[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
which applies the FWL effects to a polynomial.  
\red{above $\mathcal{P}$ was defined as a single polynomial, now it is a space of polynomials. actually space of polynomials form specific algebraic structures, called diods -- we should have used those ... }
$\mathcal{P}^{n}$ is the
space of polynomials of $n$-th order and $\mathcal{P}^{n}\langle I,F
\rangle$ is is the space of polynomials with coefficients in
$\mathbb{R}\langle I,F \rangle$.
%
%, \red{[explain index n! why do you need to work on a Euclidean domain?]}. 
%
\red{[above you introduced a notation for poly ratios, which now you do not use?]}
Thus, the perturbed controller model $\hat{C}(z)$ may be obtained from the
original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ as follows:
%
\begin{equation}
\hat{C}(z)=\frac{\mathit{FWL}[N_{C}(z)]}{\mathit{FWL}[D_{C}(z)]}.
\end{equation}
%
In the case of a synthesised controller, because the synthesis is performed
using FWL, $\hat{C}(z) \equiv C(z)$.

>>>>

Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$
(\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$ which come from tolerances/imprecisions in the original model), errors in the numeric
calculations, or roundoffs in the quantisation.  These uncertainties are 
parametrically expressed by additive terms, resulting in a uncertain model
$\hat{G}(z)$, such that:
%
\begin{equation}
\hat{G}(z)=\frac{G_n(z)+\Delta G_n(z)}{G_d(z)+\Delta G_d(z)},
\end{equation}
%
which will be represented by the following transfer function:
%
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}} : N_G \geq M_G .
\end{equation}
%
Due to the nature of the methods we use for the stability check, we require
that the parametric errors in the plant have the same polynomial order as
the plant itself (all other errors described in this paper are ensured to fulfil this property in our
implementation).

In order to simplify the presentation, we employ a notation based on the
coefficients of the polynomials.  Let $\mathcal{P}^{N}$ be a polynomial
domain of order $N$. Let $P \in \mathcal{P}^{M,N}$ be a rational polynomial
$\frac{P_n}{P_d}$, where $P_n \in \mathcal{P}^{M}$ and $P_d \in \mathcal{P}^{N}$.  
For a vector of coefficients
%
\begin{equation}
\vec{P} \in \mathbb{R}^{N+M+2}=[n_{0}\ n_{1}\ \hdots \ n_{M}\ d_{0}\ d_{1}\ \hdots\ d_{N}\ ]^T
\label{eq:coefficients}
\end{equation}
%
and an uncertainty vector 
%
\begin{equation}
\Delta{\vec{P}}=[\Delta{n}_{0}\ \Delta{n}_{1}\ \hdots \ \Delta{n}_{M}\ \Delta{d}_{0}\ \Delta{d}_{1}\ \hdots\ \Delta{d}_{N}\ ]^T \; 
\label{eq:delta_coefficients}
\end{equation}
%
we write $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$.   
In the following we will either represent the functions $G(z)$, $C(z)$, 
or work over their respective coefficients $\vec{G}, \vec{C}$ in vector form.

@@

A typical digital control system system with a continuous plant and a discrete
controller is illustrated in Figure~\ref{fig:sampledsystem}.  The DAC and
ADC converters introduce quantisation errors which are modeled as noises $\nu_{1}(z)$ and $\nu_{2}(z)$,
$G(s)$ is the continuous-time plant model with parametric additive
uncertainty $\Delta_p{G}_n(s)$ and $\Delta_p{G}_d(s)$, $R(z)$ is the reference signal, $U(z)$ is
the control signal, and $\hat{Y}(z)$ is the output signal affected by the
noises and uncertainties in the closed-loop system.

@@

%
In Figure~\ref{fig:digsystem1}, two sources of uncertainties are
illustrated: parametric uncertainties related to modelling errors, and
uncertainties introduced by quantisations in sampling and holding process,
i.e., ADC and DAC conversions.  Assuming linearity and independence between
these sources, the uncertain model may be rewritten as a vector of coefficients in the z-domain using equations \ref{eq:coefficients} and \ref{eq:delta_coefficients}
%
\begin{equation}
\label{eq:complete_unc_model}
\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q \vec{G},
\end{equation}
%
where $\Delta_p \vec{G}$ is the term that corresponds to the parametric
uncertainties and $\Delta_q \vec{G}$ is the term that reflects the
quantisation effects on the plant model.

@@

Let $\hat{C}(z)$ be the transfer function of the digital controller
represented using this FWL with integer size $I$ and fractional size~$F$. 
We shall denote the FWL domain of coefficients as $\mathbb{R}\langle I,F
\rangle$
%
%Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
%domain, {\it i.e.} a Fixed-Point Finite Word Length with integer size $I$ and fractional
%size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
%
and assume that there exists a function
$\mathit{FWL}_n[\cdot]:\mathcal{P}^{n}\rightarrow \mathcal{P}^{n}\langle I,F \rangle$,
which applies the FWL effects to a polynomial, with an equivalent $\mathit{FWL}_{n,m}[\cdot]:\mathcal{P}^{n,m}\rightarrow \mathcal{P}^{n,m}\langle I,F \rangle$ that apllies the same effect to a ratio of polynomials, where
$\mathcal{P}^{n}$ is the
space of polynomials of $n$-th order, $\mathcal{P}^{n}\langle I,F
\rangle$ is is the space of polynomials with coefficients in
$\mathbb{R}\langle I,F \rangle$, and $\mathcal{P}^{n,m}$,  $\mathcal{P}^{n,m}\langle I,F
\rangle$ are their rational equivalent.

\red{[above you introduced a notation for poly ratios, which now you do not use?]}
Thus, the perturbed controller model $\hat{C}(z)$ may be obtained from the
original model $C(z)=\frac{C_{n}(z)}{C_{d}(z)}$ as follows:
%
\begin{equation}
\hat{C}(z)=\mathit{FWL}_{M_C,N_C}[C(z)]=\frac{\mathit{FWL}_{M_C}[C_n(z)]}{\mathit{FWL}_{N_C}[C_d(z)]}.
\end{equation}
%
In the case of a synthesised controller, because the synthesis is performed
using FWL, $\hat{C}(z) \equiv C(z)$.
